### 2008-10-06 trunk/Papers/rmrs-08/conclusion.tex
Monday update

In this paper, we have motivated and defined \rmrs---a semantic
framework that has been used to represent, compare, and combine
semantic information computed from deep and shallow parsers.  \rmrs\
is designed to be maximally flexible on the type of semantic
information that can be left underspecified, so that
the semantic output of a shallow parser needn't over-determine or
under-determine the semantic information that can be extracted from
the shallow syntactic analysis.  This lays the formal foundations for
a semantic representation formalism that is emerging as a standard in
robust semantic processing.

We then defined the concept of \emph{solved forms} of an \rmrs, in
analogy to dominance graphs.  Solved forms abstract away from
irrelevant differences between models, and have been a crucial concept
in the development of efficient solvers for dominance graphs.  In the
future, we hope to draw upon that body of literature to develop
efficient algorithms for processing \rmrs s, including solvers which
will compute fully specific semantic representations from an \rmrs,
efficient inference algorithms, and algorithms for entailment
checking.  We have argued that entailment is a central notion in
comparing the outputs of different {\sc nlp} tools, and provided a syntactic
characterization for \rmrs\ entailment, which we hope will allow us to
develop efficient entailment algorithms in the future.

>>>>

In this paper, we have motivated and defined \rmrs---a semantic
framework that has been used to represent, compare, and combine
semantic information computed from deep and shallow parsers.  \rmrs\
is designed to be maximally flexible on the type of semantic
information that can be left underspecified, so that
the semantic output of a shallow parser needn't over-determine or
under-determine the semantics that can be extracted from
the shallow syntactic analysis.  This lays the formal foundations for
a formalism that is emerging as a standard in
robust semantic processing.

We then defined the concept of \emph{solved forms} of an \rmrs, in
analogy to dominance graphs.  Solved forms abstract away from
irrelevant differences between models, and have been a crucial concept
in the development of efficient solvers for dominance graphs.  In the
future, we hope to draw upon that body of literature to develop
efficient algorithms for processing \rmrs s, including solvers which
will compute fully specific semantic representations from an \rmrs,
efficient inference algorithms, and algorithms for entailment
checking.  We have argued that entailment is a central notion in
comparing the outputs of different {\sc nlp} tools, and provided a syntactic
characterisation for \rmrs\ entailment, which we hope will allow us to
develop efficient entailment algorithms in the future.

### 2008-10-06 trunk/Papers/rmrs-08/entailment.tex
Monday update

\section{RMRS comparison as entailment}
\label{sec:entailment}

The definitions in the previous section serve an important theoretical
purpose in that they provide a formal underpinning for \rmrs, which so
far has been used for partial semantic representations in implemented
systems despite the lack of a formal definition.  Next to the peace of
mind that comes with the use of a formally understood formalism, a
clean definition can also provide a foundation for the development of
efficient algorithms; this has been shown in the past in the dominance
graph literature, most recently \newcite{KolRegTha08}.  We hope that
this paper can likewise provide a starting point for the development
of efficient solvers and inference mechanisms for \rmrs.

On the other hand, the above definition of \rmrs\ provides new
concepts which can help us phrase questions of practical grammar
engineering in well-defined formal terms.  For instance, one crucial
issue in developing a hybrid system that combines the outputs of deep
and shallow processors is to determine whether the \rmrs s produced by
the two systems are compatible.  Because we assume that the deep
grammar is more informative than that of the shallow processor, this
amounts to checking whether every piece of information in the shallow
representation is consistent with what the deep grammar said.  In
general, it isn't even obvious what ``consistency'' is supposed to
mean exactly, given that variables might be renamed, $\ARG$ roles
assigned in different ways, and structural relations underspecified.
But given the formal definition of \rmrs, we can now propose that an
\rmrs\ $\varphi'$ that was computed by a shallow processor is
consistent with an \rmrs\ $\varphi$ that was computed by a deep
grammar amounts to checking \emph{entailment} between the two \rmrs s,
i.e.\ whether $\varphi \models \varphi'$.  If we could establish
efficiently that $\varphi'$ is entailed by $\varphi$, this would tell
us that all models that satisfy $\varphi$ are also models of
$\varphi'$, i.e.\ the deep representation is formally more specific.

We cannot provide an efficient algorithm for testing entailment in
this paper.  However, we propose the following novel syntactic
characterization of entailment.

@@

\begin{thm}\label{thm:big-one}
  Let $\varphi, \varphi'$ be two {\sc rmrs}s.  Then $\varphi \models
  \varphi'$ iff for every solved form $S$ of $\varphi$, there is a
  solved form $S'$ of $\varphi'$ such that $S$ is an extension of
  $S'$. \todo{Check proof holds for this version.}
% Do we have a proof where $\varphi$ and $\varphi'$ can vary on
% alphabetic variance on nodes and base variables?
\end{thm}
\begin{proof}[Proof (sketch)]
``$\Leftarrow$'' follows from
Props.~\ref{prop:solved-forms-are-satisfiable} and
\ref{prop:models-satisfy-solved-forms}.

@@

This characterization does not by itself provide an efficient test for
entailment because the number of solved forms of $\varphi$ and
$\varphi'$ may be exponential, and thus it is infeasible to compute
them all and then test for extensions.  Nevertheless, we hope that the
theorem provides a first step towards an improved understanding of
entailment that will lead to such an efficient algorithm in the
future.

>>>>

\section{RMRS Comparison as Entailment}
\label{sec:entailment}

The definitions from Section~\ref{sec:rmrs} serve an important theoretical
purpose in that they provide a formal underpinning \rmrs's existing use
for partial semantic representations in implemented
systems.  Next to the peace of
mind that comes with the use of a formally understood formalism, a
clean definition can also provide a foundation for the development of
efficient algorithms; this has been shown in the past in the dominance
graph literature, most recently \newcite{KolRegTha08}.  We hope that
this paper can likewise provide a starting point for the development
of efficient solvers and inference mechanisms for \rmrs.

On the other hand, the above definition of \rmrs\ provides new
concepts which can help us phrase questions of practical grammar
engineering in well-defined formal terms.  For instance, one crucial
issue in developing a hybrid system that combines the outputs of deep
and shallow processors is to determine whether the \rmrs s produced by
the two systems are compatible.  Because we assume that the deep
grammar is more informative than that of the shallow processor, this
amounts to checking whether every piece of information in the shallow
representation is consistent with what the deep grammar said.  In
general, it isn't even obvious what ``consistency'' is supposed to
mean exactly, given that variables might be renamed, $\ARG$ roles
assigned in different ways, and structural relations underspecified.
But given the formal definition of \rmrs, we can now propose that an
\rmrs\ $\varphi'$ that was computed by a shallow processor is
consistent with an \rmrs\ $\varphi$ that was computed by a deep
grammar if $\varphi$ entails $\varphi'$ (i.e., $\varphi \models
\varphi'$).  If we could establish 
efficiently that $\varphi'$ is entailed by $\varphi$, this would tell
us that all models that satisfy $\varphi$ are also models of
$\varphi'$, i.e.\ the deep representation is formally more specific.

We cannot provide an efficient algorithm for testing entailment in
this paper.  However, we propose the following novel syntactic
characterisation of entailment.

@@

\begin{thm}\label{thm:big-one}
  Let $\varphi, \varphi'$ be two {\sc rmrs}s.  Then $\varphi \models
  \varphi'$ iff for every solved form $S$ of $\varphi$, there is a
  solved form $S'$ of $\varphi'$ such that $S$ is an extension of
  $S'$. 
\end{thm}
\begin{proof}[Proof (sketch)]
``$\Leftarrow$'' follows from
Props.~\ref{prop:solved-forms-are-satisfiable} and
\ref{prop:models-satisfy-solved-forms}.

@@

This characterisation does not by itself provide an efficient test for
entailment because the number of solved forms of $\varphi$ and
$\varphi'$ may be exponential, and thus it is infeasible to compute
them all and then test for extensions.  Nevertheless, we hope that the
theorem provides a first step towards an improved understanding of
entailment that will lead to such an efficient algorithm in the
future.

### 2008-10-06 trunk/Papers/rmrs-08/introduction.tex
Monday update

Representing semantics as a logical form that supports automated
inference and model construction is vital for deeper language
engineering tasks, such as dialogue systems.  Logical forms
can be obtained from hand-crafted deep grammars
\cite{butt:etal:1999,copestake:flickinger:2000}, but this
tends to lack robustness: hand-crafted grammars fail to cover all
words and linguistic constructions and by design they do not handle
ill-formed phrases.

On the other hand, there has been a recent trend towards systems for
robust wide-coverage semantic construction.  For instance,
\newcite{bos:etal:2004} exploit {\sc ccg}'s syntax-semantics
interface to produce a unique logical form for each derivation of a
statistical {\sc ccg} parser; \newcite{zettlemoyer:collins:2007} and
others learn string-to-logical-form mappings, exploting informative
features from shallow language processors; and
\newcite{copestake:2003} and \newcite{frank:2004} endow robust
language processors with semantic components.

@@

There are certain semantic phenomena that these robust
approaches don't capture reliably, including quantifier scope,
optional arguments, and long-distance dependencies (for instance,
\newcite{clark:etal:2004} report that the parser used by
\newcite{bos:etal:2004} yields only 63\% accuracy on object
extraction; e.g., {\em the man that I met\dots}).  Forcing a shallow
parser to make a decision about these phenomena can therefore be
error-prone.  Depending on the application, it may be preferrable to
give the parser the option to leave a semantic decision open when it's not
sufficiently informed---i.e., to compute a partial semantic
representation and to complete it later, using information
extraneous to the parser.

In this paper, we focus on an approach to representing partial
semantic information that supports this strategy: Robust Minimal
Recursion Semantics (\rmrs, \cite{copestake:2003}).  \rmrs\ is a
generalisation of \mrs\ \cite{copestake:etal:2005} that is designed to
support underspecification of scope and predicate-argument structure.
It is an emerging standard for representing partial
semantic information, and has been applied in several implemented
systems.  For instance, \newcite{copestake:2003} and
\newcite{frank:2004} use it to specify semantic components to shallow
parsers ranging in depth from {\sc pos} taggers to chunk parsers and
intermediate parsers such as {\sc rasp} \cite{briscoe:etal:2006}.
{\sc mrs} analyses derived from deep grammars, such as the English
Resource Grammar ({\sc erg}, \cite{copestake:flickinger:2000}) are
special cases of {\sc rmrs}.

@@

Robost language processors that produce a single conventional logical
form for a given natural language string are beginning to emerge
(e.g.,
\cite{bos:etal:2004,rupp:etal:2000,wong:mooney:2006,zettlemoyer:collins:2005}).
But the output of these systems don't relate to any gold standard deep
parse as produced by expert grammar developers (for instance, while
the training corpus used in \cite{zettlemoyer:collins:2005} features
control phenomena in the language strings, their logical forms don't
represent it).  This makes it hard to judge the logical forms that the
models derive from a linguistic perspective; nor can one integrate
their output with that of a hand-crafted grammar when desired.

>>>>

Representing semantics as a logical form that supports automated
inference and model construction is vital for deeper language
engineering tasks, such as dialogue systems.  Logical forms
can be obtained from hand-crafted deep grammars
\cite{butt:etal:1999,copestake:flickinger:2000}, but this
tends to lack robustness: hand-crafted grammars fail to cover all
words and linguistic constructions and by design they do not handle
ill-formed phrases. 
There has thus been a trend recently towards systems for
robust wide-coverage semantic construction.  For instance,
\newcite{bos:etal:2004} exploit {\sc ccg}'s syntax-semantics
interface to produce a unique logical form for each derivation of a
statistical {\sc ccg} parser; \newcite{zettlemoyer:collins:2007} and
others learn string-to-logical-form mappings, exploiting informative
features from shallow language processors; and
\newcite{copestake:2003} and \newcite{frank:2004} endow shallow
language processors with semantic components.

@@

There are certain semantic phenomena that these robust
approaches don't capture reliably, including quantifier scope,
optional arguments, and long-distance dependencies (for instance,
\newcite{clark:etal:2004} report that the parser used by
\newcite{bos:etal:2004} yields 63\% accuracy on object
extraction; e.g., {\em the man that I met\dots}).  Forcing a robust
parser to make a decision about these phenomena can therefore be
error-prone.  Depending on the application, it may be preferable to
give the parser the option to leave a semantic decision open when it's not
sufficiently informed---i.e., to compute a partial semantic
representation and to complete it later, using information
extraneous to the parser.

In this paper, we focus on an approach to representing partial
semantic information that supports this strategy: Robust Minimal
Recursion Semantics (\rmrs, \cite{copestake:2003}).  \rmrs\ is
designed to
support underspecification of scope and predicate-argument structure.
It is an emerging standard for representing partial
semantic information, and has been applied in several implemented
systems.  For instance, \newcite{copestake:2003} and
\newcite{frank:2004} use it to specify semantic components to shallow
parsers ranging in depth from {\sc pos} taggers to chunk parsers and
intermediate parsers such as {\sc rasp} \cite{briscoe:etal:2006}.
{\sc mrs} analyses \cite{copestake:etal:2005}
derived from deep grammars, such as the English
Resource Grammar ({\sc erg}, \cite{copestake:flickinger:2000}) are
special cases of {\sc rmrs}.

@@

Robust language processors that produce a single conventional logical
form for a given natural language string are beginning to emerge
(e.g.,
\cite{bos:etal:2004,rupp:etal:2000,wong:mooney:2006,zettlemoyer:collins:2005}).
But the output of these systems don't relate to any gold standard deep
parse as produced by expert grammar developers (for instance, while
the training corpus used in \cite{zettlemoyer:collins:2005} features
control phenomena in the language strings, their logical forms don't
represent it).  This makes it hard to judge the logical forms that the
models derive from a linguistic perspective; nor can one integrate
their output with that of a hand-crafted grammar when desired.

### 2008-10-06 trunk/Papers/rmrs-08/motivation.tex
Monday update

This sentence exhibits several kinds of ambiguity, including a scope
ambiguity between ``every fat cat'' and ``some dog'' and lexical
ambiguities of the words ``cat'' and ``dog'' (which have 8 and 7 noun
senses according to Wordnet, respectively).  Simplifying slightly by
ignoring tense information (but see
Section~\ref{sec:extensions}), two of these readings are
shown as logical forms below; they can be represented as trees as
shown in Fig.~\ref{fig:1}.

@@

Now imagine that we are trying to extract semantic information from
the output of a part-of-speech tagger by using the word lemmas as
lexical predicate symbols.  Such a semantic representation is highly
partial, as it will not say anything about predicate-argument
relations or resolve lexical ambiguity---it will use predicate
symbols such as $\sempred{\_cat\_n}$, which might resolve to the
predicate symbols $\sem{\_cat\_n\_1}$ or $\sem{\_cat\_n\_2}$ in the
complete semantic representation.  (Notice that we are using different
fonts for the ambiguous and unambiguous predicate symbols.)  
We can
express this information in \rmrs\ as follows.

\begin{examples}
\item \label{ex:cat-pos}
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$
\end{examples}

This \rmrs\ consists of six \emph{elementary predications} ({\sc ep}s), one
for each word lemma in the sentence; each of them is prefixed by a
\emph{label} and an \emph{anchor}, which are essentially variables
that refer to nodes in the trees in Fig.~\ref{fig:1}.  
The lack of semantic dependencies rendered by a {\sc pos} tagger
also means we have unique arguments to each
predicate symbol (e.g., see $x_1$ and $x_3$ in (\ref{ex:cat-pos}),
compared with the {\em same} variable $x$ in the semantic
representations (\ref{ex:fat-cat-1}) and (\ref{ex:fat-cat-2})).
We can say that
the two trees \emph{satisfy} this \rmrs\ because it is possible to map
the labels and anchors into nodes in each tree and variable names like
$x_1$ and $x_3$ into variable names in the tree in such a way that the
predication
of
the node that labels and anchors are mapped to is consistent with the
that given in the {\sc ep}s of the {\sc rmrs}.
For instance, the first tree satisfies
the \rmrs\ because we can map $l_1$ and $a_1$ to the root of that
tree, $x_1$ (and $x_3$) are both mapped to $x$, and the root label
$\sem{\_every\_q\_1}$ is consistent with the 
{\sc ep} predicate $\sempred{\_every\_q}$.

@@

\begin{examples}
\item 
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
\hspace*{0.1in} $\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$\\
$x_3=x_4$, $x_5=x_7$
\label{ex:cat-partial-parser}
\end{examples}

@@

Finally, \rmrs\ (\ref{ex:cat-erg}) is a notational variant of the {\sc
  mrs} derived by the {\sc erg}, a wide-coverage deep grammar:
\begin{examples}
\item $l_1:a_1\handel\mbox{\_every\_q\_1}(x_1),$\\
\hspace*{0.1in}$\mbox{RSTR}(a_1,h_2),
\mbox{BODY}(a_1,h_3)$\\ 
$l_{41}:a_{41}\handel\mbox{\_fat\_j\_1}(e'), \ARG1(a_{41},x_2)$\\
$l_{42}:a_{42}\handel\mbox{\_cat\_n\_1}(x_3)$\\
$l_5:a_5\handel\mbox{\_chase\_v\_1}(e)$,\\
\hspace*{0.1in}$\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6\handel\mbox{\_some\_q\_1}(x_6)$,\\
\hspace*{0.1in}$\mbox{RSTR}(a_6,h_7),
\mbox{BODY}(a_6,h_8)$\\ 
$l_9:a_9\handel\mbox{\_dog\_n\_1}(x_7)$\\
$h_2=_q l_{42}, l_{41}=l_{42}, h_7 =_q l_9$\\
$x_1=x_2, x_2=x_3, x_3=x_4,$\\
$x_5=x_6, x_5=x_7$
\label{ex:cat-erg}
\end{examples}
RSTR and BODY are conventional names for the scopal arguments to
predicate symbols corresponding to quantifiers.   
Atoms like $h_2 \qeq l_{42}$ specify
a kind of ``outscopes'' relationship between the hole and the label,
and can be used to underspecify the scope of the two quantifiers.
Notice also that the labels of the {\sc ep}s for ``fat'' and ``cat'' are
stipulated to be equal in the \rmrs\ (\ref{ex:cat-erg}), whereas the
anchors are not. 
In the tree, it is the anchors that are mapped to the nodes with the
labels $\sem{\_fat\_a\_1}$ and $\sem{\_cat\_n\_1}$; the label is
mapped to the conjunction node just above them.  In other words, the
role of the anchor in an {\sc ep} is to connect a predicate to its
arguments, while the role of the label is to connect the {\sc ep} to the
surrounding formula.  Representing conjunction with label sharing
stems from \mrs\ and provides compact semantic representations.
Finally, (\ref{ex:cat-erg}) intuitively represents more specific
semantic information than (\ref{ex:cat-partial-parser}), so long as
the base-language constructors that \_cat\_n\_1 can correspond to is a
subset of those that \_cat\_n can correspond to (written
$\mbox{\_cat\_n\_1}\sqsubseteq \mbox{\_cat\_n}$), and similalry for
\_fat\_j\_1 etc.  This is because with these so-called SPEC relations
on the predicate symbols in place, (\ref{ex:cat-erg}) simply adds
ARGs, qeqs and variable equalities to (\ref{ex:cat-partial-parser}).

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It generalizes \mrs\ in that it can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower {\sc nlp} tool was able to provide.  \rmrs\ is
designed to serve as a generic formalism for partial semantic
representations which abstracts over the details of different {\sc nlp}
tools and allows us to represent, process, and compare information
from different tools in the same formalism, and in the long run
provide a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}) or
(\ref{ex:cat-erg}).

However, although people have started using \rmrs\ in their
implemented systems, it is still relatively ad-hoc in that its formal
syntax is not consistent across different papers, and its formal
semantics is not defined; we don't know, formally, what an \rmrs\
\emph{means} in terms of semantic representations like
(\ref{ex:fat-cat-1}) and (\ref{ex:fat-cat-2}), and this hinders our
ability to come up with efficient algorithms for processing \rmrs. The
purpose of this paper is to lay the groundwork for fixing this problem.

>>>>

This sentence exhibits several kinds of ambiguity, including a scope
ambiguity between ``every fat cat'' and ``some dog'' and lexical
ambiguities of the nouns ``cat'' and ``dog'' (which have 8 and 7 
WordNet senses respectively).  Simplifying slightly by
ignoring tense information (but see
Section~\ref{sec:extensions}), two of these readings are
shown as logical forms below; they can be represented as trees as
shown in Fig.~\ref{fig:1}.

@@

Now imagine trying to extract semantic information from
the output of a part-of-speech tagger by using the word lemmas as
lexical predicate symbols.  Such a semantic representation is highly
partial, as it will not say anything about predicate-argument
relations or resolve lexical ambiguity---it will use predicate
symbols such as $\sempred{\_cat\_n}$, which might resolve to the
predicate symbols $\sem{\_cat\_n\_1}$ or $\sem{\_cat\_n\_2}$ in the
complete semantic representation.  (Notice the different
fonts for the ambiguous and unambiguous predicate symbols.)  
We can
express this information in \rmrs\ as follows.

\begin{examples}
\item \label{ex:cat-pos}
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_j}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$
\end{examples}

This \rmrs\ consists of six \emph{elementary predications} ({\sc ep}s), one
for each word lemma in the sentence; each of them is prefixed by a
\emph{label} and an \emph{anchor}, which are essentially variables
that refer to nodes in the trees in Fig.~\ref{fig:1}.  
The lack of semantic dependencies rendered by a {\sc pos} tagger
means we have unique arguments to each
predicate symbol (e.g., see $x_1$ and $x_3$ in (\ref{ex:cat-pos}),
compared with the {\em same} variable $x$ in the semantic
representations (\ref{ex:fat-cat-1}) and (\ref{ex:fat-cat-2})).
We can say that
the two trees \emph{satisfy} this \rmrs\ because it is possible to map
the labels and anchors into nodes in each tree and variable names like
$x_1$ and $x_3$ into variable names in the tree in such a way that the
predication
of
the node that labels and anchors are mapped to is consistent with
that given in the {\sc ep}s of the {\sc rmrs}.
For instance, the first tree satisfies
the \rmrs\ because $l_1$ and $a_1$ can map to the root of that
tree and $x_1$ to $x$, and the root label
$\sem{\_every\_q\_1}$ is consistent with the 
{\sc ep} predicate $\sempred{\_every\_q}$.

@@

\begin{examples}
\item 
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_j}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
\hspace*{0.1in} $\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$\\
$x_3=x_4$, $x_5=x_7$
\label{ex:cat-partial-parser}
\end{examples}

@@

Finally, \rmrs\ (\ref{ex:cat-erg}) is a notational variant of the {\sc
  mrs} derived by the {\sc erg}, a wide-coverage deep grammar:
\begin{examples}
\item $l_1:a_1\handel\mbox{\_every\_q\_1}(x_1),$\\
\hspace*{0.1in}$\mbox{RSTR}(a_1,h_2),
\mbox{BODY}(a_1,h_3)$\\ 
$l_{41}:a_{41}\handel\mbox{\_fat\_j\_1}(e'), \ARG1(a_{41},x_2)$\\
$l_{42}:a_{42}\handel\mbox{\_cat\_n\_1}(x_3)$\\
$l_5:a_5\handel\mbox{\_chase\_v\_1}(e)$,\\
\hspace*{0.1in}$\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6\handel\mbox{\_some\_q\_1}(x_6)$,\\
\hspace*{0.1in}$\mbox{RSTR}(a_6,h_7),
\mbox{BODY}(a_6,h_8)$\\ 
$l_9:a_9\handel\mbox{\_dog\_n\_1}(x_7)$\\
$h_2=_q l_{42}, l_{41}=l_{42}, h_7 =_q l_9$\\
$x_1=x_2, x_2=x_3, x_3=x_4,$\\
$x_5=x_6, x_5=x_7$
\label{ex:cat-erg}
\end{examples}
RSTR and BODY are conventional names for the scopal arguments to
predicate symbols corresponding to quantifiers.   
Atoms like $h_2 \qeq l_{42}$ specify
a kind of ``outscopes'' relationship between the hole and the label,
and can be used to underspecify the scope of the two quantifiers.
Notice also that the labels of the {\sc ep}s for ``fat'' and ``cat'' are
stipulated to be equal in the \rmrs\ (\ref{ex:cat-erg}), whereas the
anchors are not. 
In the tree, it is the anchors that are mapped to the nodes with the
labels $\sem{\_fat\_j\_1}$ and $\sem{\_cat\_n\_1}$; the label is
mapped to the conjunction node just above them.  In other words, the
role of the anchor in an {\sc ep} is to connect a predicate to its
arguments, while the role of the label is to connect the {\sc ep} to the
surrounding formula.  Representing conjunction with label sharing
stems from \mrs\ and provides compact semantic representations.
Finally, (\ref{ex:cat-erg}) intuitively represents more specific
semantic information than (\ref{ex:cat-pos}), so long as
the constructors that \_cat\_n\_1 can correspond to is a
subset of those that \_cat\_n can correspond to (written
$\mbox{\_cat\_n\_1}\sqsubseteq \mbox{\_cat\_n}$), and similarly for
\_fat\_j\_1 etc.  This is because with these so-called SPEC relations
on the predicate symbols in place, (\ref{ex:cat-erg}) simply adds
ARGs, qeqs and variable equalities to (\ref{ex:cat-pos}).

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower {\sc nlp} tool can provide.  \rmrs\ is
designed to be a generic formalism for partial semantic
representations which abstracts over the details of different {\sc nlp}
tools and allows us to represent, process, and compare information
from different tools in the same formalism, and in the long run
provide a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}) or
(\ref{ex:cat-erg}).

However, although people have started using \rmrs\ in their
implemented systems, it is still relatively ad-hoc in that its formal
syntax is not consistent across different papers, and its formal
semantics is not defined; we don't know, formally, what an \rmrs\
\emph{means} in terms of semantic representations like
(\ref{ex:fat-cat-1}) and (\ref{ex:fat-cat-2}), and this hinders our
ability to design efficient algorithms for processing \rmrs. The
purpose of this paper is to lay the groundwork for fixing this problem.
